Untitled

### 2022-09-29 Supplementary_Material/Bees_and_other_func_grous_separated.Rmd
edits

d1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1))) + geom_point(data = dat_analysis, aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4") +  coord_cartesian(ylim=c(1,100),clip="off") +
ylab("Number of visits") +
theme_ms() + 
theme(legend.position = "none",plot.subtitle=element_text(size=30,face="bold")) +
labs(title = "", subtitle =my_y_title) +
annotate(geom = "text", x = -1.7, y =-32 , label = "High flower N.", size = 8) +
annotate(geom = "text", x = -1.72, y =-42 , label = "Small flowers", size = 8) + 
annotate(geom = "text", x = 1.8, y =-32 , label = "Low flower N.", size = 8) + 
annotate(geom = "text", x = 1.8, y =-42 , label = "Large flowers", size = 8) +
xlab("") +
annotate(geom = "text", x = -0.1, y =-20 , label = "Flower number - Flower size axis", size = 8.5, fontface =2) + xlab("") + theme(panel.border=element_rect(color="black",size=1.2))

@@

d2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = dat_analysis, aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4") + 
coord_cartesian(ylim=c(1,100),clip="off") +
ylab("") + 
theme_ms() + 
theme(legend.position = "none")  +
theme(plot.title = element_text(size = 36, face = "bold"),plot.subtitle=element_text(size=30,face="bold")) + labs(title = "", subtitle = my_y_title) +
annotate(geom = "text", x = -1.7, y =-32 , label = "Low poll. depend.", size = 8) +
annotate(geom = "text", x = -1.65, y =-42 , label = "Small floral display", size = 8) + 
annotate(geom = "text", x = 1.75, y =-32 , label = "High poll. depend.", size = 8) + 
annotate(geom = "text", x = 1.8, y =-42 , label = "Large floral display", size = 8) +
xlab(NULL) +
annotate(geom = "text", x = -0.1, y =-20 , label = "Pollinator dependence - Floral display axis", size = 8.5, fontface =2) +
theme(panel.border=element_rect(color="black",size=1.2))

@@

d3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = dat_analysis, aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4") + 
coord_cartesian(ylim=c(1,100),clip="off") +
ylab("") + 
theme_ms() + 
theme(legend.position = "none",plot.subtitle=element_text(size=30,face="bold")) + labs(title = "", subtitle = my_y_title) +
annotate(geom = "text", x = -1.6, y =-32 , label = "Short styles", size = 8) +
annotate(geom = "text", x = -1.2, y =-42 , label = "High poll. depend.", size = 8) + 
annotate(geom = "text", x = 1.95, y =-32 , label = "Long styles", size = 8) + 
annotate(geom = "text", x = 2.3, y =-42 , label = "Low poll. depend.", size = 8) +
xlab(" \n \n  ") +
annotate(geom = "text", x = 0.25, y =-20 , label = "Style length - Pollinator dependence axis", size = 8.5, fontface =2) +
theme(panel.border=element_rect(color="black",size=1.2))

>>>>

d1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1))) + geom_point(data = dat_analysis, aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4") +  coord_cartesian(ylim=c(1,100),clip="off") +
ylab("Number of visits") +
theme_ms() + 
theme(legend.position = "none",plot.subtitle=element_text(size=30,face="bold")) +
labs(title = "", subtitle =my_y_title) +
annotate(geom = "text", x = -1.69, y =-32 , label = "High flower N.", size = 8) +
annotate(geom = "text", x = -1.72, y =-42 , label = "Small flowers", size = 8) + 
annotate(geom = "text", x = 1.8, y =-32 , label = "Low flower N.", size = 8) + 
annotate(geom = "text", x = 1.8, y =-42 , label = "Large flowers", size = 8) +
xlab("") +
annotate(geom = "text", x = -0.1, y =-20 , label = "Flower number - Flower size axis", size = 8.5, fontface =2) + xlab("") + theme(panel.border=element_rect(color="black",size=1.2))

@@

d2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1))) + geom_point(data = dat_analysis, aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4") + 
coord_cartesian(ylim=c(1,100),clip="off") +
ylab("") + 
theme_ms() + 
theme(legend.position = "none")  +
theme(plot.title = element_text(size = 36, face = "bold"),plot.subtitle=element_text(size=30,face="bold")) + labs(title = "", subtitle = my_y_title) +
annotate(geom = "text", x = -1.77, y =-32 , label = "High aut. selfing", size = 8) +
annotate(geom = "text", x = -1.65, y =-42 , label = "Small floral display", size = 8) + 
annotate(geom = "text", x = 1.6, y =-32 , label = "Low aut. selfing", size = 8) + 
annotate(geom = "text", x = 1.8, y =-42 , label = "Large floral display", size = 8) +
xlab(NULL) +
annotate(geom = "text", x = -0.1, y =-20 , label = "Autonomous selfing - Floral display axis", size = 8.5, fontface =2) +
theme(panel.border=element_rect(color="black",size=1.2))

@@

d3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1))) + geom_point(data = dat_analysis, aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.5, color="brown4") + geom_line(size=1.4, color="brown4") + 
coord_cartesian(ylim=c(1,100),clip="off") +
ylab("") + 
theme_ms() + 
theme(legend.position = "none",plot.subtitle=element_text(size=30,face="bold")) + labs(title = "", subtitle = my_y_title) +
annotate(geom = "text", x = -1.6, y =-32 , label = "Short styles", size = 8) +
annotate(geom = "text", x = -1.35, y =-42 , label = "Low aut. selfing", size = 8) + 
annotate(geom = "text", x = 1.95, y =-32 , label = "Long styles", size = 8) + 
annotate(geom = "text", x = 2.25, y =-42 , label = "High aut. selfing", size = 8) +
xlab(" \n \n  ") +
annotate(geom = "text", x = 0.25, y =-20 , label = "Style length - Autonomous selfing axis", size = 8.5, fontface =2) +
theme(panel.border=element_rect(color="black",size=1.2))

### 2022-09-29 Supplementary_Material/Species_Level_Metric_Pcs.Rmd
edits

Specialization_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC1, y = d),
  size = 3.5, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab("Specialization (d')") + xlab("PC1") + ggtitle(NULL, subtitle = "(g)") +  xlab("High flower N.    Low flower N.\nSmall flowers    Large flowers")

@@

Specialization_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC2, y = d),
  size = 3.5, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab(NULL) + xlab("PC2") + ggtitle(NULL, subtitle = "(h)") + xlab("Low poll. depend.   High poll. depend.")

@@

Specialization_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y = (estimate__))) + geom_point(data = data_analysis_2,aes(x = -PC3, y = d),
 size = 3.5, alpha=0.65, colour="darkorange3") + ylim(0,quantile(data_analysis_2$d, 0.95)) +theme_ms()+geom_line(colour="black",size=1.5)+
  geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + ylab(NULL) + xlab("PC3") + ggtitle(NULL, subtitle = "(i)")+ xlab("Short styles      Long styles\n High poll. depend.   Low poll. depend.")

>>>>

Specialization_PC1 <- ggplot(ce_1[[1]], aes(x = -PC1, y = (estimate__))) + 
geom_point(data = data_analysis_2,aes(x = -PC1, y = d),
           size = 3.5, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + coord_cartesian(ylim=c(0,quantile(data_analysis_2$d, 0.95)), 
            clip="off") + 
           theme_ms() +
geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, 
            alpha=0.1,fill="black") + ylab("Specialization (d')") + 
xlab("PC1") + 
ggtitle(NULL, subtitle = "(g)") +  
annotate(geom = "text", x = -1.6, y =-0.3 , 
               label = "High flower N.", size = 8) +
annotate(geom = "text", x = -1.65, y =-0.41 ,
               label = "Small flowers", size = 8) + 
annotate(geom = "text", x = 1.75, y =-0.3 , 
               label = "Low flower N.", size = 8) + 
annotate(geom = "text", x = 1.75, y =-0.41 ,
               label = "Large flowers", size = 8) +
annotate(geom = "text", x = 0.10, y =-0.19 , 
    label = "Flower number - Flower size axis", size = 8.5, fontface =2) +
theme(panel.border=element_rect(color="black",size=1.2)) +
xlab(" \n \n  ")

@@

Specialization_PC2 <- ggplot(ce_2[[1]], aes(x = -PC2, y =
(estimate__))) + 
geom_point(data = data_analysis_2,aes(x = -PC2, y = d),
           size = 3.5, alpha=0.65, colour="darkorange3") + geom_line(colour="black",size=1.5) + coord_cartesian(ylim=c(0,quantile(data_analysis_2$d, 0.95)), 
                clip="off") +
theme_ms() +
geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1,fill="black") + 
ylab(NULL) + 
xlab("PC2") + 
ggtitle(NULL, subtitle = "(h)") + 
xlab(NULL) +
annotate(geom = "text", x = -1.57, y =-0.3 , 
               label = "High aut. selfing", size = 8) +
annotate(geom = "text", x = -1.45, y =-0.41 ,
               label = "Small floral display", size = 8) + 
annotate(geom = "text", x = 1.75, y =-0.3 , 
               label = "Low aut. selfing", size = 8) + 
annotate(geom = "text", x = 1.9, y =-0.41 ,
               label = "Large floral display", size = 8) +
annotate(geom = "text", x = 0.10, y =-0.19 , 
    label = "Autonomous selfing - Floral display axis", size = 8.5, fontface =2) +
theme(panel.border=element_rect(color="black",size=1.2))

@@

Specialization_PC3 <- ggplot(ce_3[[1]], aes(x = -PC3, y =             (estimate__))) + 
geom_point(data = data_analysis_2,aes(x = -PC3, y = d),
           size = 3.5, alpha=0.65, colour="darkorange3")  +
theme_ms() + 
geom_line(colour="black",size=1.5) +
geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2,    
            alpha=0.1,fill="black") +
ylab(NULL) + 
xlab("PC3") + 
coord_cartesian(ylim=c(0,quantile(data_analysis_2$d, 0.95)), 
                clip="off") +
ggtitle(NULL, subtitle = "(i)") + 
annotate(geom = "text", x = -1.57, y =-0.3 , 
         label = "Short styles", size = 8) +
annotate(geom = "text", x = -1.35, y =-0.41 ,
         label = "Low aut. selfing", size = 8) + 
annotate(geom = "text", x = 2.05, y =-0.3 , 
         label = "Long styles", size = 8) + 
annotate(geom = "text", x = 2.3, y =-0.41 ,
         label = "High aut. selfing", size = 8) +
annotate(geom = "text", x = 0.25, y =-0.19 , 
         label = "Style length - Autonomous selfing axis", 
         size = 8.5, fontface =2) +
theme(panel.border=element_rect(color="black",size=1.2)) +
xlab(NULL)

### 2022-09-29 Supplementary_Material/Sup_Mat_Lanuza_et_al_2022.Rmd
edits

  plot <- plot + xlab(paste("Flower number - Flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
  plot <- plot + ylab(paste("Pollinator dependence - Floral display ", "(",(percentage[2]),"%",")", sep = "")) #YLAB

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Fig. S6.} Phylogenetically informed principal component analysis (pPCA) for all plant species with the first (flower number - flower size axis) and third (style length - pollinator dependence axis) principal component that explained most trait variation."}
setwd("~/R_Projects/Reproductive Traits")

@@

  plot <- plot + xlab(paste("Flower number - Flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
  plot <- plot + ylab(paste("Style length - Pollinator dependence axis ", "(",(percentage[3]),"%",")", sep = "")) #YLAB

>>>>

  plot <- plot + xlab(paste("Flower number - Flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
  plot <- plot + ylab(paste("Autonomous selfing - Floral display ", "(",(percentage[2]),"%",")", sep = "")) #YLAB

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=10, fig.cap="\\textbf{Fig. S6.} Phylogenetically informed principal component analysis (pPCA) for all plant species with the first (flower number - flower size axis) and third (style length - autonomous selfing) principal component that explained most trait variation."}
setwd("~/R_Projects/Reproductive Traits")

@@

  plot <- plot + xlab(paste("Flower number - Flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
  plot <- plot + ylab(paste("Style length - Autnomous selfing axis ", "(",(percentage[3]),"%",")", sep = "")) #YLAB
